\section{Response to Reviewer \#1}
\subsection*{Overall Comments}
\begin{mdframed}
	\begin{quote}
		Reviewer \# 1 - Good paper. Talk briefly about side channel attacks. Address the comments below for another revision.
	\end{quote}
\end{mdframed}

\subsection{Response}

We greatly value your detailed feedback and careful review. In response to your suggestions, we have expanded our discussion on side channel attacks. Additionally, we have included relevant references to support this new content. We trust that these revisions satisfactorily address your concerns.

\noindent\rule{\linewidth}{2.0pt}

\subsection{Reviewer Comment}
\begin{mdframed}
	\begin{quote}
		Reviewer \# 1.1 - References are not uniformly formatted
	\end{quote}
\end{mdframed}

\subsection{Response}
We appreciate your feedback. We have meticulously reviewed the .bib file and the references, and made the necessary adjustments to ensure uniform formatting. We believe these revisions adequately address the concerns.

\noindent\rule{\linewidth}{2.0pt}

\subsection{Reviewer Comment}
\begin{mdframed}
	\begin{quote}
		Reviewer \# 1.2 - Please add comparisons in a table (or subsection) so that one could fairly compare your work with similar previous works.
	\end{quote}
\end{mdframed}

\subsection{Response}
% TODO add specific table, need add the table in the response
Thank you for your suggestion. In response, we have added a new table in the Results section of our revised manuscript. This table offers a comprehensive comparison between our work and similar previous studies. We trust that this addition effectively addresses your concerns.

\noindent\rule{\linewidth}{2.0pt}

\subsection{Reviewer Comment}
\begin{mdframed}
	\begin{quote}
		Reviewer \# 1.3 - Papers related to crypto need to consider this: With the advent of post-quantum cryptography, it is better to add some relevant papers including the followings to make sure you cover that topic too. When PQC replaces ECC/RSA every security application from smart phones to block chains will be affected.
	\end{quote}
\end{mdframed}

\subsection{Response}

We value your feedback. Accordingly, we've added a discussion about post-quantum cryptography in the Introduction section of our updated manuscript. To support this new content, we've also included pertinent references. We believe these modifications adequately address your concerns. The detailed revisions are as follows:


\color{blue}
% TODO replace introduction with PQC discussion

XXXX detailed revisions XXXX


	[xx] High-performance fault diagnosis schemes for efficient hash algorithm blake, 2019 IEEE 10th Latin American Symposium on Circuits \& Systems (LASCAS).

	[xx] CRC-oriented error detection architectures of post-quantum cryptography niederreiter key generator on FPGA, 2022 IEEE Nordic Circuits and Systems Conference (NorCAS), 2022.

	[xx] Error Detection Schemes Assessed in FPGA for Multipliers in Lattice-Based Key Encapsulation Mechanisms in post-quantum cryptography, IEEE Transactions on Emerging Topics in Computing, 2022.

	[xx] Hardware Constructions for Error Detection in WG-29 Stream Cipher Benchmarked on FPGA, IEEE Transactions on Computer-Aided Design of Integrated Circuits and Systems, 2023, to appear.

\color{black}

\noindent\rule{\linewidth}{2.0pt}

\subsection{Reviewer Comment}
\begin{mdframed}
	\begin{quote}
		Reviewer \# 1.4 - Again, any crypto paper needs to address this: Also add some previous works on side-channel attacks and lightweight cryptography or PQC.
	\end{quote}
\end{mdframed}

\subsection{Response}
% TODO add SCA content of Introduction

We appreciate your expert suggestion. In response, we have expanded our discussion to include previous works on side-channel attacks and have added relevant references to support this content. We trust that these modifications adequately address your concerns. The detailed revisions are as follows:

\color{blue}
detailed content of SCA in Introduction

[xx] Education and Research Integration of Emerging Multidisciplinary Medical Devices Security, American Society for Engineering Education (ASEE), 2016.

[xx] Multidisciplinary Approaches and Challenges in Integrating Emerging Medical Devices Security Research and Education, American Society for Engineering Education (ASEE), 2016.

[xx] Fault Detection Schemes for High Performance VLSI Implementations of the Advanced Encryption Standard, The University of Western Ontario, 2007.

\color{black}


\noindent\rule{\linewidth}{6.0pt}